---
title       : Investment Asset Class Performance Analysis
subtitle    : 
author      : Yours Truly Anonymous
job         : 
framework   : io2012        # {io2012, html5slides, shower, dzslides, ...}
highlighter : highlight.js  # {highlight.js, prettify, highlight}
hitheme     : tomorrow      # 
widgets     : []            # {mathjax, quiz, bootstrap}
mode        : selfcontained # {standalone, draft}
knit        : slidify::knit2slides
---

## Objective

- Visually compare performance of investment asset classes over time  
- Compare performance over maximum available time range (1998 thru 2013)  
- Compare performance during dotcom bust  
- Compare performance during great recession  
- Data is intended as input for constructing diverified portfolio for minimizing volatility and maximizing return  

```{r miscCode, echo=FALSE,warning=FALSE,cache=FALSE}
library(reshape2)
library(ggplot2)

normalize <- function(df) {
        dfn=melt(df,id="Year")
        names(dfn)[2]="Asset.class"
        names(dfn)[3]="Return"
        dfn$Asset.class=as.factor(dfn$Asset.class)
        return(dfn)
}

dosummaryplot <- function(dfn, yearfrom, yearto) {
        gtitle = paste("Asset class performance for period", as.character(yearfrom), "through", as.character(yearto))
        dfnx = dfn[(dfn$Year >= yearfrom & dfn$Year <= yearto), ];
        plt=ggplot(dfnx, aes(x=Asset.class, y=Return, fill=Asset.class)) + geom_boxplot() +
                stat_summary(fun.y=mean, geom="point", shape=5, size=4) +
                scale_x_discrete("Asset Class",
                                 labels=c("Smallcap Stock","Value Stock","Largecap Stock","Growth Stock",
                                          "Real Estate Stock","Foreign Developed Stock","Hi Yield Bond",
                                          "Investment Grade Bond","Emerging Market Stock","Commodity"))+
                scale_y_continuous("Return (percent)",breaks=c(-60,-55,-50,-45,-40,-35,-30,-25,-20,-15,-10,-5,0,5,10,15,20,25,30,35,40,45,50,55,60))+
                ggtitle(gtitle)
        #print(plt)
        #ggsave(filename="asset-perf-summary.png",plot=plt)
        return(plt)
}

df = read.csv("/Users/vinay/datasciencecoursera/class8/project/asset-class-performance-1998-thru-2013.csv")
dfn <- normalize(df)
minYear = dfn[1,1]
maxYear = dfn[nrow(dfn),1]

```


--- .class #id 

## Performance 1998-2013

```{r perfall,echo=FALSE,warning=FALSE,cache=FALSE}
dosummaryplot(dfn, 1998, 2013)
```


--- .class #id 

## Performance 2000-2002

```{r perfdotcom,echo=FALSE,warning=FALSE,cache=FALSE}
dosummaryplot(dfn, 2000, 2002)
```


--- .class #id 

## Performance 2008-2010

```{r perfgreatrecession,echo=FALSE,warning=FALSE,cache=FALSE}
dosummaryplot(dfn, 2008, 2010)
```


---

